Generality in food webs scales with species richness not not with latitude

### 2015-06-14 manuscript/latitudepaper.tex
Abstract is single spaced for prettier fit

\textwidth 16cm 
\textheight 21cm
\footskip 1.0cm

\title{Generality in food webs scales with species richness not not with latitude}
\author{Alyssa R. Cirtwill$^{1,2}$, Daniel B. Stouffer$^{1}$, Tamara N. Romanuk$^{2}$}
\date{$^1$School of Biological Sciences\\University of Canterbury\\
Private Bag 4800\\Christchurch 8140, New Zealand}
\medskip$^2$Department of Biology\\Life Science Centre\\
Dalhousie University\\1355 Oxford St.\\P0 BOX 15000\\
Halifax, NS B3H 4R2\\Canada\\}

\begin{document}
\maketitle
\baselineskip=8.5mm

\vspace{0.4 in}

\section*{Abstract}

Several properties of food webs---the networks of feeding links between
species---vary systematically with the species richness of the underlying
community.  Under the ``latitude-niche breadth hypothesis'', which predicts
that species in the tropics will tend to evolve narrower niches, one might
expect that these scaling relationships could also be affected by latitude. To
test this hypothesis, we analysed the scaling relationships between species
richness and average generality, vulnerability, and links per species across a
set of 163 empirical food webs.  We also investigated scaling relationships
between the three food-web properties and the proportions of the web made up 
by basal resources, intermediate consumers, and top predators. While we
observed no effect of latitude on scaling relationships in the estuarine,
marine, and terrestrial food webs, there were strong effects of latitude on
scaling relationships in the freshwater food webs. In these communities,
the latitude-niche breadth hypothesis appears to hold true while in other habitat
types niches appear to be broader in the tropics. These contrasting findings
indicate that it is important to account for habitat type when exploring gradients
in food-web structure.

@@

\begin{figure}[H]
\includegraphics[width=.9\textwidth]{Figures/by_TL/scaling_with_S/proportions/fitlines_nonts.eps}
\caption{Scaling relationships for link density, generality (number of prey), 
and vulnerability (number of predators) 
against the proportions of basal resources (\% Basal), intermediate consumers (\% Intermediate), top 
predators (\% Top), and species richness of a food web. 
For each relationship we show observed values corrected for
ecosystem type and latitude (grey circles), as well as the overall scaling relationship (N=163 food webs). }
\label{props_v_lat}
\end{figure}

@@

>>>>

\textwidth 16cm 
\textheight 21cm
\footskip 1.0cm
\begin{document}

\title{Generality in food webs scales with species richness not not with latitude}
\author{Alyssa R. Cirtwill$^{1,2}$, Daniel B. Stouffer$^{1}$, Tamara N. Romanuk$^{2}$}
\date{$^1$School of Biological Sciences\\University of Canterbury\\
Private Bag 4800\\Christchurch 8140, New Zealand \\
\medskip$^2$Department of Biology\\
Life Science Centre, Dalhousie University\\1355 Oxford St., P0 BOX 15000\\
Halifax NS, B3H 4R2\\ Canada\\}

\maketitle
\baselineskip=8.5mm

\vspace{0.3 in}

\begin{spacing}{1.0}
\section*{Abstract}

Several properties of food webs---the networks of feeding links between
species---vary systematically with the species richness of the underlying
community.  Under the ``latitude-niche breadth hypothesis'', which predicts
that species in the tropics will tend to evolve narrower niches, one might
expect that these scaling relationships could also be affected by latitude. To
test this hypothesis, we analysed the scaling relationships between species
richness and average generality, vulnerability, and links per species across a
set of 163 empirical food webs.  We also investigated scaling relationships
between the three food-web properties and the proportions of the web made up 
by basal resources, intermediate consumers, and top predators. While we
observed no effect of latitude on scaling relationships in the estuarine,
marine, and terrestrial food webs, there were strong effects of latitude on
scaling relationships in the freshwater food webs. In these communities,
the latitude-niche breadth hypothesis appears to hold true while in other habitat
types niches appear to be broader in the tropics. These contrasting findings
indicate that it is important to account for habitat type when exploring gradients
in food-web structure.
\end{spacing}

@@

\begin{figure}[H]
\includegraphics[width=.9\textwidth]{Figures/by_TL/scaling_with_S/proportions/fitlines_nonts.eps}
\caption{Scaling relationships for link density, generality (number of prey), 
and vulnerability (number of predators) 
against the proportions of basal resources (\% Basal), intermediate consumers (\% Intermediate), top 
predators (\% Top), and species richness of a food web. 
For each relationship, we show observed values corrected for
ecosystem type and latitude (grey circles), as well as the overall scaling relationship (N=163 food webs). }
\label{props_v_lat}
\end{figure}

@@

>>>>>>> 7787e1ad724c4c9aa740fb54fce5a4669c120daf
